---
title: "Data Wrangling Exercise 1"
author: "Tadaaki Sun"
output: html_document
---

## Load the Data in RStudio
Imported refine_original.csv in RStudio and view to check.

```{r}
View(refine_original_csv)
```

Converting data into data frame called "refine"
```{r}
refine <- read.csv("refine_original.csv.csv")
```

Quick checks for converting to data frame
```{r}
refine
str(refine)
```

Load necessary packages: dplyr,stringr,tidyr
```{r}
install.packages("dplyr")
install.packages("stringr")
install.packages("tidyr")
```

## Clean up brand names
```{r}
refine$company <- tolower(refine$company)
refine$company <- str_replace(refine$company, "phillips","philips")
refine$company <- str_replace(refine$company, "phllips","philips")
refine$company <- str_replace(refine$company, "phillps","philips")
refine$company <- str_replace(refine$company, "fillips","philips")
refine$company <- str_replace(refine$company, "phlips","philips")
refine$company <- str_replace(refine$company, "akz0","akzo")
refine$company <- str_replace(refine$company, "ak zo","akzo")
refine$company <- str_replace(refine$company, "unilver","unilever")
refine
```

## Separate product code and number
```{r}
refine$`Product code / number`<- separate(refine,`Product code / number`,c("product.code", "number",sep="-"))
refine2 <- refine$`Product code / number`
```

## Add product categories
```{r}
refine2$product.category <- str_replace(refine2$product.code, "p","Smartphone")
refine2$product.category2 <- str_replace(refine2$product.category, "v","TV")
refine2$product.category3 <- str_replace(refine2$product.category2, "x","Laptop")
refine2$product.category4 <- str_replace(refine2$product.category3, "q","Tablet")
refine2$product.category <- refine2$product.category4
refine2$product.category2 <- NULL
refine2$product.category3 <- NULL
refine2$product.category4 <- NULL
```

## Add full address for geocoding
```{r}
refine2$full.address <- unite(refine2, full.address,c(address,city,country),sep=",")
refine3 <- refine2$full.address
```

## Create dummy variables for company and product category
```{r}
refine3$number <- as.numeric(refine3$number)
summary(refine3)
refine3$company_philips <- factor(with(refine3$company_philips,ifelse((refine3$company=="philips"),1,0)))
refine3$company_akzo <- factor(with(refine3$company_akzo,ifelse((refine3$company=="akzo"),1,0)))
refine3$company_van_houten <- factor(with(refine3$company_van_houten,ifelse((refine3$company=="van_houten"),1,0)))
refine3$company_unilever <- factor(with(refine3$company_unilever,ifelse((refine3$company=="unilever"),1,0)))
refine3$product_smartphone <- factor(with(refine3$product_smartphone,ifelse((refine3$product.code=="p"),1,0)))
refine3$product_tv <- factor(with(refine3$product_tv,ifelse((refine3$product.code=="v"),1,0)))
refine3$product_laptop <- factor(with(refine3$product_laptop,ifelse((refine3$product.code=="q"),1,0)))
refine3$product_tablet <- factor(with(refine3$tablet,ifelse((refine3$product.code=="x"),1,0)))
```

## Submit the project
```{r}
write.csv(refine3,file="refine_clean.csv")
```
